The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-06-26 head.tex
test
ready for modify

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product. This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources. 
However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components come along with them, the heterogeneous of resource's type, quality, price, processing velocity leads to hard taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product. This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.
